Results Summary

### 2025-03-27 analysis.Rmd
refactor models to have access to full model

run_logistic_models <- function(design, formulas, method_name) {
  print(paste0("Estimating models: ", method_name))

  results <- list()
  roundTo <- 2
  roundP <- 3

  for (i in seq_along(formulas)) {
    if (method_name %in% c("cbps", "entropy", "bart")) {
      package <- "WeightIt"
      approach <- "ipw"
    } else if (method_name %in% c("twang_gbm")) {
      package <- "twang"
      approach <- "ipw"
    } else if (method_name == "subclass_glm") {
      package <- "MatchIt"
      approach <- "subclassification"
    } else {
      package <- "MatchIt"
      approach <- "match w/ replacement"
    }

    if (method_name == "subclass_glm") {
      # Extract subclass weights
      subclass_weights <- weights(design, type = "sampling")

      # Run weighted survey logistic regression
      model <- svyglm(formula = formulas[[i]], design = design, family = quasibinomial(), contrasts = NULL)
    } else {
      # Standard survey logistic regression
      model <- svyglm(formula = formulas[[i]], design = design, family = quasibinomial(), contrasts = NULL)
    }

@@

    result_summ <- data.frame(
      package = package,
      method = method_name,
      approach = approach,
      estimand = "ATT",
      formula = names(formulas)[i],
      estimate = estimate,
      estimate_or = or,
      se = se,
      t_value = t_value,
      p_value = p_value,
      lb_95_or = ci_lb_or,
      ub_95_or = ci_ub_or
    )

    rownames(result_summ) <- NULL
    results[[i]] <- result_summ
  }

  do.call(rbind, results)
}
```

@@

# Start with naive model results
naive_design <- svydesign(ids = ~e_mrn_deidentified, data = m_data, weights=~1)
naive_results <- run_logistic_models(naive_design, formulas, "Naive")

all_results <- list(naive_results)

# Removing CEM because matching process drops levels of certain factors due to unavailable matches.
method_names <- names(results)
method_names <- method_names[! method_names %in% c("cem")]

@@

  if(method_name %in% c("cbps", "entropy", "energy", "bart")) {
    # Weightit methods
    matched_data <- m_data
    weights <- method_result$result$weights
    matched_data$weights <- weights
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~weights, data = matched_data)
  } else if (method_name == "twang_gbm") {
    # For TWANG model with weights
    m_data$twang_att_w <- get.weights(method_result$result, stop.method = "es.mean")
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~twang_att_w, data = m_data)
  } else if(method_name == "subclass_glm") {
    matched_data <- MatchIt::match_data(method_result$result, subclass = "subclass")
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights=~weights)
    design <- postStratify(design, ~subclass, xtabs(~subclass, data = matched_data))
  }  else {
    matched_data <- MatchIt::get_matches(method_result$result)
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights=~1)
  }

  # Run logistic models and store results
  method_results <- run_logistic_models(design, formulas, method_name)
  all_results[[method_name]] <- method_results
}

# Combine all results into a single data frame
final_results <- do.call(rbind, all_results)

@@

saveRDS(final_results, file.path(ps_dir, paste0("ps_results_summary.rds")))
```

>>>>

fit_logistic_models <- function(design, formulas) {
  models <- list()
  for (i in seq_along(formulas)) {
    model <- svyglm(
      formula = formulas[[i]],
      design = design,
      family = quasibinomial(),
      contrasts = NULL
    )
    models[[names(formulas)[i]]] <- model
  }
  models
}

summarize_logistic_models <- function(models, method_name) {
  roundTo <- 2
  roundP <- 3

  results <- lapply(names(models), function(name) {
    model <- models[[name]]

@@

    package <- if (method_name %in% c("cbps", "entropy", "bart")) "WeightIt"
    else if (method_name %in% c("twang_gbm")) "twang"
    else "MatchIt"

    approach <- if (method_name %in% c("cbps", "entropy", "bart", "twang_gbm")) "ipw"
    else if (method_name == "subclass_glm") "subclassification"
    else "match w/ replacement"

    tibble::tibble(
      package = package,
      method = method_name,
      approach = approach,
      estimand = "ATT",
      formula = name,
      estimate = estimate,
      estimate_or = or,
      se = se,
      t_value = t_value,
      p_value = p_value,
      lb_95_or = ci_lb_or,
      ub_95_or = ci_ub_or
    )
  })

  bind_rows(results)
}

@@

model_objects <- list()

# Naive model first
naive_design <- svydesign(ids = ~e_mrn_deidentified, data = m_data, weights = ~1)
naive_models <- fit_logistic_models(naive_design, formulas)
naive_results <- summarize_logistic_models(naive_models, method_name = "Naive")

all_results <- list(Naive = naive_results)
model_objects$Naive <- naive_models

# Run for each method
method_names <- names(results)
method_names <- method_names[! method_names %in% c("cem")]

@@

  if (method_name %in% c("cbps", "entropy", "energy", "bart")) {
    matched_data <- m_data
    weights <- method_result$result$weights
    matched_data$weights <- weights
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~weights, data = matched_data)

  } else if (method_name == "twang_gbm") {
    m_data$twang_att_w <- get.weights(method_result$result, stop.method = "es.mean")
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~twang_att_w, data = m_data)

  } else if (method_name == "subclass_glm") {
    matched_data <- MatchIt::match_data(method_result$result, subclass = "subclass")
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~weights)
    design <- postStratify(design, ~subclass, xtabs(~subclass, data = matched_data))

  } else {
    matched_data <- MatchIt::get_matches(method_result$result)
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights = ~1)
  }

  # Run models and summaries
  models <- fit_logistic_models(design, formulas)
  model_summary <- summarize_logistic_models(models, method_name)

  model_objects[[method_name]] <- models
  all_results[[method_name]] <- model_summary
}

# Combine all summary results
final_results <- bind_rows(all_results)

@@

saveRDS(final_models, file.path(ps_dir, paste0("ps_analysis_models.rds")))
saveRDS(final_results, file.path(ps_dir, paste0("ps_results_summary.rds")))
```

### 2025-03-27 results-summary.Rmd
results summary polishing
refactor models to have access to full model

# Get results summary from the pipeline; no PHI in here
results <- readRDS(file.path(ps_dir, "ps_results_summary.rds"))

@@

fullResultsForHumans <- fullResults |> 
  mutate(
    estimate_or = estimate_or |> as.numeric(),
    se = se |> as.numeric(),
    t_value = t_value |> as.numeric(),
    p_value = p_value |> as.numeric(),
    lb_95_or = lb_95_or |> as.numeric(),
    ub_95_or = ub_95_or |> as.numeric(),
    method = case_when(
      method == "Naive" ~ "No Adjustment",
      method == "nearest_glm" ~ "Nearest Neighbor Matching, GLM (MatchIt)",
      method == "nearest_gam" ~ "Nearest Neighbor Matching, GAM (MatchIt)",
      method == "nearest_gbm" ~ "Nearest Neighbor Matching, GBM (MatchIt)",
      method == "nearest_lasso" ~ "Nearest Neighbor Matching, LASSO (MatchIt)",
      method == "nearest_mahalanobis" ~ "Nearest Neighbor Matching, Mahalanobis (MatchIt)",
      method == "nearest_rpart" ~ "Nearest Neighbor Matching, Recursive Partinioning (MatchIt)",
      method == "subclass_glm" ~ "Subclassification, GLM (MatchIt)",
      method == "cbps" ~ "IPW, Covariate Balancing Propensity Score (WeightIt)",
      method == "entropy" ~ "IPW, Entropy Balancing (WeightIt)",
      method == "bart" ~ "IPW, Bayesian Additive Regression Trees (WeightIt)",
      method == "twang_gbm" ~ "IPW, GBM (twang)",
      TRUE ~ "Unknown"
    )
  ) |> 
  select(
    method, estimand, estimate_or, se, t_value, p_value, lb_95_or, ub_95_or
  ) |> 
  rename(
    "OR" = estimate_or,
    "SE" = se,
    "t" = t_value,
    "Lower" = lb_95_or,
    "Upper" = ub_95_or
  ) |> 
  arrange(OR) |>
  mutate(method = factor(method, levels = method))

# Define colors
fullResultsForHumans$color <- "black"
fullResultsForHumans$color[fullResultsForHumans$method == "No Adjustment"] <- "red"
fullResultsForHumans$color[fullResultsForHumans$method == "IPW, GBM (twang)"] <- "blue"
```

```{r, echo = FALSE, fig.width = 10, fig.height = 8}
# Plot
plot <- ggplot(fullResultsForHumans, aes(x = reorder(method, OR), y = OR, color = color)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), size = 0.8) +
  geom_point(size = 3) +
  geom_text(aes(label = sprintf("%.2f", OR), color = color), vjust = -1.2, hjust = 0.5, size = 4) +  # Match color
  coord_flip() +
  scale_color_identity() +  # Uses the color column directly
  scale_y_continuous(breaks = seq(1, max(fullResultsForHumans$Upper), by = 0.1)) +  # Custom x-axis breaks every 0.1
  theme_minimal(base_size = 14) +
  labs(
    x = element_blank(),
    y = "Odds Ratio",
    title = "Doubly Robust Propensity Score Adjusted\n Model Estimates (ATT)",  # Wrap title
    caption = "\n\nOdds Ratio of 1.0 = No Association.
               MatchIt, WeightIt, and twang R packages are used for estimation.
               IPW Twang GBM results (shown in blue) reported throughout paper.
               No Adjustment (shown in red) reflects results with no propensity score adjustment."
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", margin = margin(b = 15)),  # Add space below title
    legend.position = "none",
    axis.line = element_line(color = "gray80"),  # Lighten axis lines
    axis.text = element_text(color = "gray30"),  # Lighten axis labels
    axis.ticks = element_line(color = "gray80"),  # Lighten axis ticks
    axis.title.x = element_text(margin = margin(t = 10)),  # Space between y-axis label and plot
    plot.caption = element_text(margin = margin(t = 15)),  # Space above caption
    plot.margin = margin(20, 20, 30, 20)  # Adds overall spacing
  ) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray70") +  # Lightened reference line
  geom_hline(yintercept = 1, color = "gray30")  # Black solid line at OR = 1

@@

tableOutput$Method <- factor(
  fullResultsForHumans$method, 
  levels = c(
    "IPW, GBM (twang)",  # Move to top
    "No Adjustment",      # Move to second
    setdiff(levels(factor(fullResultsForHumans$method)), c("IPW, GBM (twang)", "No Adjustment"))  # Keep existing order for others
  )
)

>>>>

# Get results summary from the pipeline; no PHI in here
results <- readRDS("ps_results_summary.rds")
# results <- readRDS(file.path(ps_dir, "ps_results_summary.rds"))

@@

fullResultsForHumans <- fullResults |> 
  mutate(
    estimate_or = estimate_or |> as.numeric(),
    se = se |> as.numeric(),
    t_value = t_value |> as.numeric(),
    p_value = p_value |> as.numeric(),
    lb_95_or = lb_95_or |> as.numeric(),
    ub_95_or = ub_95_or |> as.numeric(),
    method = case_when(
      method == "Naive" ~ "No Propensity Score Balancing",
      method == "nearest_glm" ~ "Nearest Neighbor Matching, GLM (MatchIt)",
      method == "nearest_gam" ~ "Nearest Neighbor Matching, GAM (MatchIt)",
      method == "nearest_gbm" ~ "Nearest Neighbor Matching, GBM (MatchIt)",
      method == "nearest_lasso" ~ "Nearest Neighbor Matching, LASSO (MatchIt)",
      method == "nearest_mahalanobis" ~ "Nearest Neighbor Matching, Mahalanobis (MatchIt)",
      method == "nearest_rpart" ~ "Nearest Neighbor Matching, Recursive Partinioning (MatchIt)",
      method == "subclass_glm" ~ "Subclassification, GLM (MatchIt)",
      method == "cbps" ~ "IPTW, Covariate Balancing Propensity Score (WeightIt)",
      method == "entropy" ~ "IPTW, Entropy Balancing (WeightIt)",
      method == "bart" ~ "IPTW, Bayesian Additive Regression Trees (WeightIt)",
      method == "twang_gbm" ~ "IPTW, GBM (twang)",
      TRUE ~ "Unknown"
    )
  ) |> 
  select(
    method, estimand, estimate_or, se, t_value, p_value, lb_95_or, ub_95_or
  ) |> 
  rename(
    "OR" = estimate_or,
    "SE" = se,
    "t" = t_value,
    "Lower" = lb_95_or,
    "Upper" = ub_95_or
  ) |> 
  arrange(OR) |>
  mutate(method = factor(method, levels = method))

# Define colors
fullResultsForHumans$color <- "black"
fullResultsForHumans$color[fullResultsForHumans$method == "No Propensity Score Balancing"] <- "red"
fullResultsForHumans$color[fullResultsForHumans$method == "IPTW, GBM (twang)"] <- "blue"
```

```{r, echo = FALSE, fig.width = 10, fig.height = 8}
# Plot
plot <- ggplot(fullResultsForHumans, aes(x = reorder(method, OR), y = OR, color = color)) +
  geom_pointrange(aes(ymin = Lower, ymax = Upper), size = 0.8) +
  geom_point(size = 3) +
  geom_text(aes(label = sprintf("%.2f", OR), color = color), vjust = -1.2, hjust = 0.5, size = 4) +
  coord_flip() +
  scale_color_identity() +
  scale_y_continuous(breaks = seq(1, max(fullResultsForHumans$Upper), by = 0.1)) +
  scale_x_discrete(expand = c(0.075, 0.075)) +
  theme_minimal(base_size = 14) +
  labs(
    x = element_blank(),
    y = "Odds Ratio",
    title = "Doubly Robust Propensity Score Adjusted\n Model Estimates (ATT)",
    caption = "\n\nOdds Ratio of 1.0 = No Association.
               MatchIt, WeightIt, and twang R packages are used for estimation.
               IPTW = Inverse probability of treatment weighting.
               IPTW Twang GBM results (shown in blue) reported throughout paper.
               No Adjustment (shown in red) reflects results with no propensity score adjustment."
  ) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", margin = margin(b = 15)),
    legend.position = "none",
    axis.line = element_line(color = "gray80"),
    axis.text = element_text(color = "gray30"),
    axis.ticks = element_line(color = "gray80"),
    axis.title.x = element_text(margin = margin(t = 10)),
    plot.caption = element_text(margin = margin(t = 15)),
    plot.margin = margin(20, 20, 30, 20)
  ) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray70") +  
  geom_hline(yintercept = 1, linetype = "dashed",  color = "gray30")

@@

tableOutput$Method <- factor(
  fullResultsForHumans$method, 
  levels = c(
    "IPTW, GBM (twang)",  # Move to top
    "No Adjustment",      # Move to second
    setdiff(levels(factor(fullResultsForHumans$method)), c("IPTW, GBM (twang)", "No Adjustment"))  # Keep existing order for others
  )
)
